Qubit tests from classical codes

### 2022-12-15 quantum_codes_test.tex
finished a first pass

\newcommand{\mA}{\ensuremath{\mathcal{A}}}
\newcommand{\mB}{\ensuremath{\mathcal{B}}}
\newcommand{\mC}{\ensuremath{\mathcal{C}}}
\newcommand{\mE}{\ensuremath{\mathcal{E}}}
\newcommand{\mD}{\ensuremath{\mathcal{D}}}
\newcommand{\mF}{\ensuremath{\mathcal{F}}}
\newcommand{\mG}{\ensuremath{\mathcal{G}}}
\newcommand{\mH}{\ensuremath{\mathcal{H}}}
\newcommand{\mK}{\ensuremath{\mathcal{K}}}
\newcommand{\mM}{\ensuremath{\mathcal{M}}}
\newcommand{\mI}{\ensuremath{\mathcal{I}}}
\newcommand{\cM}{\ensuremath{\mathcal{M}}}
\newcommand{\mQ}{\ensuremath{\mathcal{Q}}}
\newcommand{\mR}{\ensuremath{\mathcal{R}}}
\newcommand{\mS}{\ensuremath{\mathcal{S}}}
\newcommand{\mT}{\ensuremath{\mathcal{T}}}
\newcommand{\mX}{\ensuremath{\mathcal{X}}}
\newcommand{\mY}{\ensuremath{\mathcal{Y}}}

@@

@@

@@

\begin{proposition}\label{prop:sound-game}
Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$. Let $\delta,\delta':[0,1]\to[0,1]$. Then the following hold:
\begin{enumerate}
\item If $M$ has quantum soundness $\delta$ then $G_{\code,M}$ is $O(\delta)$-robust.
\item If $G_{\code,M}$ is $\delta'$-robust and $(\mC,M)$ is Abelian then $M$ has quantum soundness $O(r\delta')$. 
\end{enumerate}
\end{proposition}

\begin{proof}[Proof sketch]
We start with the second assertion. Suppose then that that $G_{\code,M}$ is $\delta'$-robust, for some function $\delta'$. Let $(\mM,A)$ be be an $r$-local $\eps$-presentation of $\code$, and for each $S\subseteq\{1,\ldots,n\}$ such that $|S|=r$, $\{B^{S,i}\}_{i\in S}$ the commuting family of projective measurements promised by the definition; then there is an isometry $w$ such that 
\[ \Es{i\in S} \sum_a \big\| A^i_a - w^* B^{S,i}_{a}w \big\|_2^2 \,\leq\,\eps_S\;.\]
 For any $a\in\field^S$ let $\tilde{P}^S_a = \prod_{i\in S} B^{S,i}_{a_i}$. Then $\{\tilde{P}^S_a\}_{a\in\field^S}$ is a projective measurement such that
\begin{align}
\Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_{a\in \field^S} \tau\big(  w^* \tilde{P}^S_a w \, A^i_{a_i}\big) 
&= \Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_{b\in \field}\tau\big(  w^* B^{S,i}_b w\, A^i_{b}\big)\notag \\
&= \Es{S\leftarrow M(\cdot)} \Es{i\in S} \frac{1}{2}\big(\tau(w^*w) + \tau(1) - \sum_{b\in \field} \big\|  w^* B^{S,i}_b w - A^i_{b}\big\|_2^2\big) \notag\\
&\geq \,1-2\eps\;.\label{eq:s-g-1}
\end{align}
Let $\{P^S_a\}$ be the family of projective measurements on $\mM$ that is promised by Lemma~\ref{lem:pull-back}. It follows that  
\begin{align}
\Es{S\leftarrow M(\cdot)} &\Es{i\in S} \sum_{b\in\field}\big\| \sum_{\substack{a\in \field^S\\a_i=b} } P^S_a - A^i_{a_i}\big\|_2^2\notag\\ 
&\leq 2\Es{S\leftarrow M(\cdot)} \Es{i\in S}\sum_{b\in\field}\big\| \sum_{\substack{a\in \field^S\\a_i=b} } w^*\tilde{P}^S_a w- A^i_{a_i}\big\|_2^2
+ 2\Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_{b\in\field}\big\| \sum_{\substack{a\in \field^S\\a_i=b} } w^*\tilde{P}^S_a w - \sum_{\substack{a\in \field^S\\a_i=b} } {P}^S_a\big\|_2^2 \notag\\
&= O(\eps)\;,\label{eq:s-g-2}
\end{align}
where in the last line the first term is bounded by~\eqref{eq:s-g-1} and the second using the guarantees of Lemma~\ref{lem:pull-back}.
Using the definition of $G_{\code,M}$,~\eqref{eq:s-g-2} can be rewritten as
\begin{equation}
 \sum_{(S,i)} \mu(S,i) \sum_{a\in \field^s}\sum_{b\in\field} D(S,i,a,b) \tau\big(  P^S_a  A^i_{b}\big) \,\geq \,1-O(\eps)\;.\label{eq:s-g-2}
\end{equation}
In other words $\omega(G_{\code,M};\strategy)\geq 1-\eps'$ for $\strategy$ the strategy with measurements $\{A^i_b\}$ and $\{P^{S}_a\}$ and some $\eps'=O(\eps)$. Using the definition of robustness we deduce that $(\mM,A,P)$ is $(\delta'(\eps'),\mu)$-close to a perfect strategy $(\mN,C,Q)$ for $G$. Specializing to the $A$ measurements, using the definition of closeness there exists a projection $P\in \mM_\infty$ and $\{C^i\}_a \subseteq P\mM_\infty P$ such that $\Es{i}\sum_a \|A^i_a-w^* C^i_a w \|_2^2 \leq 2\delta'$, and moreover $\{C^i_a\}$ satisfy that for any $S$ in the support of $\mu$, $\{C^i_a\}$ pairwise commute for $i\in S$. Using the assumption that $(\code,M)$ is Abelian, all the $\{C^i_a\}$ commute and form a representation of $\code$.

Now we show the first assertion. Suppose that $M$ has quantum soundness $\delta$.
Let $\strategy=(\mM,A,P)$ be a strategy for $G_{\code,M}$ on $(\mM,\tau)$ that succeeds with probability at least $1-\eps$. Using similar reasoning as above, $(\mM,A)$ is an $\eps'$-local presentation of code, for some $\eps'=O(\eps)$. Using quantum soundness, there is a representation $(\mN,B)$ that is $\delta'$-close, for $\delta'=\delta(\eps')$. Now, we let $Q^S_a = \prod_{i\in S} B^i_{a_i}$ which is a projective measurement on $\mN$. It is easy to verify that $(\mN,B,Q)$ is a perfect strategy in $G_{\code,M}$. Moreover $(\mN,B,Q)$ is $O(r\delta)$-close to $(\mM,A,P)$.\tnote{This last estimate is a guess and needs a calculation}
\end{proof}

@@

\begin{figure}[!htbp]
  \centering
  \begin{gamespec}
Let $M$ be an $r$-local tester for the $[n,k,d]_q$ code $\code$. 
    \begin{enumerate}
      \setlength\itemsep{1pt}
    \item (\textbf{Code test}) Select $W\in \{X,Z\}$ uniformly at random, and $\rand$ a setting for $M$'s random tape at random. Let $S=M(\rand)\subseteq\{1,\ldots,n\}$. Sample $i\in S$ uniformly at random. Send $(W,S)$ to $\alice$ and $(W,i)$ to $\bob$. Receive $a\in \field^S$ from $\alice$ and $b\in \field$ from $\bob$. Accept if and only if $M(S,a)=1$ and $a_i = b$.  
    \item (\textbf{Anti-commutation test}) Select $(i_X,i_Z)\in \{1,\ldots,n\}^2 $ uniformly at random. Let $\omega = (G_\code i_X, G_\code i_Z)$ and $\gamma =  (G_\code i_X) \cdot(G_\code {i_Z}) \in \field$.
		\begin{enumerate}
		\item If $\gamma=0$ then select a pair of questions $(x_c,y_c)$ as in the commutation game. Send $(x_c,\omega)$ to $\alice$ and $(y_c,\omega)$ to Bob. Accept if and only if their answers are accepted in the commutation game. 
		\item If $\gamma\neq 0$ then do the same but for the anti-commutation game. 
		\end{enumerate} 
		 \item (\textbf{Consistency test}) Select $\omega=(i_X,i_Z)\in \{1,\ldots,n\}^2 $ and $W\in \{X,Z\}$ uniformly at random. Let $\gamma = (G_\code i_X) \cdot(G_\code {i_Z}) \in \field$. Send $(W,i_W)$ to $\alice$ and $(x_{W,\gamma},\omega)$ to $\bob$. Receive $a\in \field$ and $b\in \field$ respectively. Accept if and only if $a=b$. 
    \end{enumerate}
  \end{gamespec}
  \caption{The braiding test over $\code$ verifies that the players respond consistently with a uniformly random codeword from $\code$, obtained by measuring $k$ shared EPR pairs in the standard or Hadamard basis and encoding the resulting $k$-bit string.}
  \label{fig:braiding-test}
\end{figure}

@@

\begin{theorem}
Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$ that is $\delta(\eps)$-quantum sound. Then the braiding test over $\code$ is a $(k,\delta')$-qubit test, where $S_X=S_Z=\{G_\code e_i:\,i\in\{1,\ldots,n\}\}\subseteq \field^k$, $\phi(W,G_\code e_i)=(W,i)$ and $\delta' = O(\delta(6\eps))$.\footnote{Assume $G_\code$ has no repeated columns.} 
\end{theorem}

\begin{proof}
\underline{Completeness:} We first verify completeness. For $W\in\{X,Z\}$ and $i\in\{1,\ldots,n\}$ let $P^{(W,i)}_a = (\tau^W(G_\code e_i))_a$ and $P^{(W,S)}_a = \prod_{i\in S} P^{(W,i)}_{a_i}$. For $\omega=(i_X,i_Z)\in \{1,\ldots,n\}^2 \times \field^2$ and $\gamma =(G_\code i_X) \cdot(G_\code {i_Z}) $ we let $P^{x_{W,\gamma},\omega} = P^{(W,i_W)}$.

@@

\underline{Soundness:} Next we show soundness. Let $\strategy$ be a synchronous strategy for $G$  in  $(\mM,\tau)$ that succeeds with probability at least $1-\eps$. For $W\in\{X,Z\}$ let $\strategy^W$ be the strategy in $G_{\code,M}$ that is obtained by restricting $\strategy$ to the relevant measurements, i.e.\ the $P^{W,S}$ and $P^{W,i}$.  Then $\strategy^W$ succeeds with probability at least $1-6\eps$ in $G_{\code,M}$. Using the assumption that $M$ is $\delta(\cdot)$-quantum sound and Lemma~\ref{lem:sound-game} it follows that there is a $\delta_1 = O(\delta(6\eps))$ such that for each $W\in\{X,Z\}$, $\strategy^W$ is $(\delta_1,\mu)$ close to a perfect strategy $\tilde{\strategy}^W$ on $(\mN^W,\tau^W)$. Since $(\code,M)$ is abelian, any perfect strategy comes from a POVM $\{\tilde{P}^W_u\}_{u\in \field^n}$ such that $\sum_{u\in \code}\tilde{P}^W_u = \Id$. 
Applying Lemma~\ref{lem:pull-back}, we obtain projective measurement $\{Q^W_u\}$ on $\mM$ such that 
\begin{equation*}
\sum_u \big\|Q^W_u - (w^W)^* \tilde{P}_u^W w^W \big\|^2_2 \,=\, O(\delta_1)\;.
\end{equation*}
Let $Q^{W,i}_b = \sum_{a: a_i=b} Q^W_u$. 
Using the triangle inequality it then follows that
\begin{equation*}
 \Es{i\in [n]}  \big\|\widehat{\tilde{P}^{W,i}} - \widehat{Q^W}(a) \big\|^2_\tau \,=\, O(\delta_1)\;.
\end{equation*}
In particular, the strategy that consists of $Q^X$, $Q^Z$, $P^{x_c,\omega}$ for $(x_c,\omega) \in \mX_{com}\times \Omega_+$ and $P^{x_{ac},\omega}$ for $(x_{ac},\omega)\in \mX_{anticom} \times \Omega_-$ succeeds in the dlS game with probability $1-O(\delta_1+\eps)$. Applying~\cite[Corollary 3.9]{de2022spectral}, the conclusion follows. 
\end{proof}

>>>>

\newcommand{\mA}{\ensuremath{\mathcal{A}}}
\newcommand{\mB}{\ensuremath{\mathcal{B}}}
\newcommand{\mC}{\ensuremath{\mathcal{C}}}
\newcommand{\mE}{\ensuremath{\mathcal{E}}}
\newcommand{\mD}{\ensuremath{\mathcal{D}}}
\newcommand{\mF}{\ensuremath{\mathcal{F}}}
\newcommand{\mG}{\ensuremath{\mathcal{G}}}
\newcommand{\mH}{\ensuremath{\mathcal{H}}}
\newcommand{\mK}{\ensuremath{\mathcal{K}}}
\newcommand{\mM}{\ensuremath{\mathcal{M}}}
\newcommand{\mI}{\ensuremath{\mathcal{I}}}
\newcommand{\mJ}{\ensuremath{\mathcal{J}}}
\newcommand{\cM}{\ensuremath{\mathcal{M}}}
\newcommand{\mQ}{\ensuremath{\mathcal{Q}}}
\newcommand{\mR}{\ensuremath{\mathcal{R}}}
\newcommand{\mS}{\ensuremath{\mathcal{S}}}
\newcommand{\mT}{\ensuremath{\mathcal{T}}}
\newcommand{\mX}{\ensuremath{\mathcal{X}}}
\newcommand{\mY}{\ensuremath{\mathcal{Y}}}

@@

\begin{lemma}\label{lem:l1-l2}
Let $\{P_i\}$ and $\{Q_i\}$ be two projective measurements such that $P$ and $Q$ are $(\eps,\mu)$-close. Then 
\begin{equation}\label{eq:l1-l2}
\sum_i \tau\big(|P_i-Q_i|\big) \,\leq\, \eps+ 2 \sqrt{\eps}\;.
\end{equation}
\end{lemma}

\begin{proof}
Write, using the triangle inequality, 
\begin{align*}
 \sum_i \tau\big(|P_i - w^* Q_i w|\big) &\leq\, \sum_i \tau\big(|(P_i-P_i^2)|\big) + \tau\big(|P_i(P_i-w^*Q_iw)|\big) + \tau\big(|(P_i-w^*Q_iw)w^*Q_iw|\big) \\
&\qquad +\tau\big(| (w^*Q_iw^*wQ_iw-w^*Q_iw)|\big)\;.
\end{align*}
The first term on the right-hand side is zero, because $P$ is assumed projective. The terms in the middle are bounded using H\"older's inequality. The last term can be written as 
\begin{align*}
\sum_i \tau\big(| (w^*Q_iw^*wQ_iw-w^*Q_iw)|\big) &= \sum_i \tau\big( (w^*Q_i(1-w^*w)Q_iw)\big)\\
&=  \tau\Big( (1-w^*w)\Big(\sum_i Q_iww^* Q_i\Big)\Big)\\
&\leq \tau(1-w^*w) \Big\|\sum_i Q_iww^* Q_i\Big\|\\
&\leq \eps\;.
\end{align*}
\end{proof}

\begin{lemma}\label{lem:dp}
Let $\{P_i\}$ and $\{Q_i\}$ be two POVM on $(\mM,\tau)$ with the same index set. Then for any $f:\mI\to \mJ$, 
\begin{equation}\label{eq:dp}
\sum_{j\in \mJ} \Big\| \sum_{i\in f^{-1}(j)} (P_i-Q_i) \Big\|_2^2 \,\leq\, \sum_{i\in \mI} \big\| P_i-Q_i\big\|_2^2\;.
\end{equation}
\end{lemma}

\begin{proof}
This follows by expending the left-hand side and using $\tau(P_iQ_j)\geq 0$ for all $i\neq j$. 
\end{proof}

@@

The next lemma shows that close strategies have close value.

\begin{lemma}\label{lem:close-value}
Let $G=(\mX,\mu,\mA,D)$ be a game and $\strategy=\{P^x_a\}$ and $\strategy'=\{Q^x_a\}$ strategies on $\mM$ and $\mN$ respectively such that $\{P^x_a\}$ and $\{Q^x_a\}$ are $(\eps,\mu)$-close. Then 
\[ \big|\omega(G;\strategy) - \omega(G;\strategy')\big|\,\leq\, O\big(\sqrt{\eps}\big)\]
\end{lemma}

\begin{proof}
By definition,
\begin{align*}
\omega(G;\strategy') &= \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y)  \tau\big( Q^x_a \, Q^y_b \big)\\
&=  \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y)  \tau\big( w^* Q^x_a w\, w^* Q^y_b w\big)\\
&\quad+  \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y)  \tau\big( w^* Q^x_a (P - w\, w^* ) Q^y_b w\big)
+ \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y)  \tau\big( Q^x_a  Q^y_b (P-ww^*)\big)
\end{align*}
The second and third term on the right-hand side can be bonded as
\begin{align*}
\Big|\Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y)  \tau\big( w^* Q^x_a (P - w\, w^* ) Q^y_b w\big)\Big|
&=\Big| \tau\Big(  (P - w\, w^* )\Big( \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y) Q^y_b ww^* Q^x_a \Big)\Big)\Big|\\
&\leq \tau(P-ww^*) \Big\|\Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y) Q^y_b ww^* Q^x_a \Big\|\\
&\leq \eps\;,
\end{align*}
where the first inequality is by H\"older's inequality and the last inequality uses the definition of closeness and $\|A\circ B\| \leq \max_{i,j} |A_{i,j}|\|B\|$, with $A = \sum_{a,b} D(a,b) P_{a,b}$, with $P_{a,b} = \sum_{i,j} \bra{u_{i,a}} \ket{v_{j,b}}$ with $\ket{u_{i,a}}$ a basis for the range of $Q^x_a$ and $\ket{v_{j,b}}$ for the range of $Q^y_b$, and $B=\sum_{a,b} Q^y_b ww^* Q^x_a = ww^*$.

For $x\in \mX$ such that $\mu(x)\neq 0$, denote by $\mu_x$ the (symmetrized) conditional distribution $\mu_x(y)=\frac{1}{2}(\mu(x,y)+\mu(y,x))/\mu(x)$. Then
\begin{align*}
\big|\omega(G;\strategy) - \omega(G;\strategy')\big|
 &\leq \eps+ \Big|\Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y) \big( \tau\big( P^x_a \, P^y_b \big)-\tau\big( w^* Q^x_a w\, w^* Q^y_b w\big)\big)\Big|\\
&\leq  \eps+ \Big|\Es{x\sim\mu} \sum_{a}  \tau\Big( \big(P^x_a-w^* Q^x_aw\big) \, \Big( \Es{y\sim \mu_x} \sum_b D(a,b,x,y) P^y_b \Big)\Big)\Big|\\
&\qquad+ \Big|\Es{y\sim\mu} \sum_{b}  \tau\Big(\Big( \Es{x\sim \mu_y} \sum_a D(a,b,x,y) w^* Q^x_a w\Big) \big(P^y_b-w^*Q^y_bw\big) \, \Big)\Big|\\
&\leq \eps+2\Es{x\sim\mu} \sum_{a}  \tau\big(\big| P^x_a-w^*Q^x_aw\big|\big) \\
&\leq \eps+4\sqrt{\eps}\;,
\end{align*}
where the third line uses $\tau(AB)\leq\tau(|A|)\|B\|$ and the last inequality is by~\eqref{eq:l1-l2} and Jensen's inequality.
\end{proof}

@@

\begin{proposition}\label{prop:sound-game}
Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$. Let $\delta,\delta':[0,1]\to[0,1]$. Then the following hold:
\begin{enumerate}
\item If $M$ has quantum soundness $\delta$ then $G_{\code,M}$ is $\delta''$-robust, for some $\delta''(\eps)=O(r\sqrt{\delta(2\eps)})$. 
\item If $G_{\code,M}$ is $\delta'$-robust and $(\mC,M)$ is Abelian then $M$ has quantum soundness $\delta''$, for some $\delta''(\eps) = O(\delta'(\sqrt{\eps}))$. 
\end{enumerate}
\end{proposition}

\begin{proof}[Proof sketch]
We start with the second assertion. Suppose then that $G_{\code,M}$ is $\delta'$-robust, for some function $\delta'$. Let $(\mM,A)$ be be an $r$-local $\eps$-presentation of $\code$, and for each $S\subseteq\{1,\ldots,n\}$ such that $|S|=r$, $\{B^{S,i}\}_{i\in S}$ the commuting family of projective measurements promised by the definition. Then for every $S$ then there is a projection $P^S$ in $\mM_\infty$ and an isometry $w^S\in P^S \mM_\infty 1_\mM$ such that 
\[ \Es{i\in S} \sum_a \big\| A^i_a - (w^S)^* B^{S,i}_{a}w^S \big\|_2^2 \,\leq\,\eps_S\;,\]
for some $(\eps_S)$ such that $\Es{S\leftarrow M(\cdot)} \eps_S \leq \eps$. 
 For any $a\in\field^S$ let $\tilde{P}^S_a = \prod_{i\in S} B^{S,i}_{a_i}$. Then $\{\tilde{P}^S_a\}_{a\in\field^S}$ is a projective measurement such that
\begin{align}
\Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_{a\in \field^S} \tau\big(  (w^S)^* \tilde{P}^S_a w^S \, A^i_{a_i}\big) 
&= \Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_{b\in \field}\tau\big(  (w^S)^* B^{S,i}_b w^S\, A^i_{b}\big)\notag \\
&= \Es{S\leftarrow M(\cdot)} \Es{i\in S} \frac{1}{2}\Big(\tau\big((w^S)^*w^S\big) + \tau(1) - \sum_{b\in \field} \big\|  (w^S)^* B^{S,i}_b w^S - A^i_{b}\big\|_2^2\Big) \notag\\
&\geq \,\frac{1}{2}(1-\eps+1-\eps)\;.\label{eq:s-g-1}
\end{align}
Let $\{P^S_a\}$ be the family of projective measurements on $\mM$ that is promised by Lemma~\ref{lem:pull-back}, so that by a simple averaging argument,
\begin{equation}\label{eq:s-g-1b}
\Es{S\leftarrow M(\cdot)}\sum_a \big\| P^S_a - (w^S)^* \tilde{P}^S_a (w^S)\big\|_2^2 \,=\, O(\eps)\;. 
\end{equation}
We can write
\begin{align}
\Big|\Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_a \tau\big( P^S_a A^i_{a_i}\big)
&- \Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_a \tau\big( (w^S)^* \tilde{P}^S_a (w^S)A^i_{a_i}\big)\Big|\notag\\
&= \Big| \Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_a \tau\big(\big((w^S)^* \tilde{P}^S_a (w^S)-P^S_a\big)A^i_{a_i}\big)\Big|\notag\\
&\leq \Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_a \tau\big(\big|(w^S)^* \tilde{P}^S_a (w^S)-P^S_a\big|\big)\\
&= O(\sqrt{\eps})\;,\label{eq:s-g-2}
\end{align}
where the second line uses $\|A^i_a\|\leq 1$ and the last is by Lemma~\ref{lem:l1-l2} and~\eqref{eq:s-g-1b}.
Together with~\eqref{eq:s-g-1} and using the definition of $G_{\code,M}$, we have shown that
\begin{equation}
 \sum_{(S,i)} \mu(S,i) \sum_{a\in \field^s}\sum_{b\in\field} D(S,i,a,b) \tau\big(  P^S_a  A^i_{b}\big) \,\geq \,1-O(\sqrt{\eps})\;.\label{eq:s-g-2}
\end{equation}
In other words $\omega(G_{\code,M};\strategy)\geq 1-\eps'$ for $\strategy$ the strategy with measurements $\{A^i_b\}$ and $\{P^{S}_a\}$ and some $\eps'=O(\sqrt{\eps})$. Using the definition of robustness we deduce that $(\mM,A,P)$ is $(\delta'(\eps'),\mu)$-close to a perfect strategy $(\mN,C,Q)$ for $G$. Specializing to the $A$ measurements, using the definition of closeness there exists a projection $P\in \mM_\infty$ and $\{C^i\}_a \subseteq P\mM_\infty P$ such that $\Es{i}\sum_a \|A^i_a-w^* C^i_a w \|_2^2 \leq 2\delta'$, and moreover $\{C^i_a\}$ satisfy that for any $S$ in the support of $\mu$, $\{C^i_a\}$ pairwise commute for $i\in S$. Using the assumption that $(\code,M)$ is Abelian, all the $\{C^i_a\}$ commute and form a representation of $\code$.

Now we show the first assertion. Suppose that $M$ has quantum soundness $\delta$.
Let $\strategy=(\mM,A,P)$ be a strategy for $G_{\code,M}$ on $(\mM,\tau)$ that succeeds with probability at least $1-\eps$. This can be reformulated as 
\begin{equation}
 \sum_{(S,i)} \mu(S,i) \sum_{a\in \field^s}\sum_{b\in\field} D(S,i,a,b) \tau\big(  P^S_a  A^i_{b}\big) \,\geq \,1-\eps\;.\label{eq:s-g-3}
\end{equation}
For each $S$ and $i\in S$, let $B^{S,i}_b = \sum_{a:a_i=b} P^S_a$. Then using the definition of $\mu$ and $D$, rewriting~\eqref{eq:s-g-3} immediately gives
\begin{equation}
 \Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_{b\in\field} \big\| A^i_{b} - B^{S,i}_b\big\|_2^2 \,\leq \,2\eps\;.\label{eq:s-g-3}
\end{equation}
Thus $(\mM,A)$ is an $\eps'$-local presentation of code, for $\eps'=2\eps$. Using quantum soundness, there is a representation $(\mN,C)$ of $\code$ that is $\delta'$-close to $(\mM,A)$, for $\delta'=\delta(\eps')$.

For every $S$, let $Q^S_a = \prod_{i\in S} C^i_{a_i}$, which is a projective measurement on $\mN$. It is easy to verify that $(\mN,C,Q)$ is a perfect strategy in $G_{\code,M}$. Moreover,
\begin{align}
\Es{S\leftarrow M(\cdot)} \sum_{a\in\field^k} \big\| P^S_a - w^* Q^S_a w\big\|_2^2
&=2 - 2\Es{S\leftarrow M(\cdot)} \sum_{a\in\field^k} \tau\Big( \prod_i B^{S,i}_{a_i} w^* \prod_i C^{i}_{a_i}w\big)\label{eq:s-g-4}
\end{align}
Applying a simple inductive argument, using Lemma~\ref{lem:l1-l2} we get that
\begin{align*}
\Big|\Es{S\leftarrow M(\cdot)} \sum_{a\in\field^k} \tau\Big( \prod_i B^{S,i}_{a_i} w^* \prod_i C^{i}_{a_i}w\big) - \Es{S\leftarrow M(\cdot)} \sum_{a\in\field^k} \tau\Big( \prod_i B^{S,i}_{a_i}  \prod_i B^{S,i}_{a_i}\big)\Big| &= O\big(r\sqrt{\delta'}\big)\;.
\end{align*}
Since the second term on the left-hand side above equals $1$, plugging back into~\eqref{eq:s-g-4} it follows that   $(\mN,B,Q)$ is $O(r\sqrt{\delta'})$-close to $(\mM,A,P)$.
\end{proof}

@@

\begin{figure}[!htbp]
  \centering
  \begin{gamespec}
Let $M$ be an $r$-local tester for the $[n,k,d]_q$ code $\code$. 
    \begin{enumerate}
      \setlength\itemsep{1pt}
    \item (\textbf{Code test}) Select $W\in \{X,Z\}$ uniformly at random, and $\rand$ a setting for $M$'s random tape at random. Let $S=M(\rand)\subseteq\{1,\ldots,n\}$. Sample $i\in S$ uniformly at random. Send $(W,S)$ to $\alice$ and $(W,i)$ to $\bob$. Receive $a\in \field^S$ from $\alice$ and $b\in \field$ from $\bob$. Accept if and only if $M(S,a)=1$ and $a_i = b$.  
    \item (\textbf{Anti-commutation test}) Select $(i_X,i_Z)\in \{1,\ldots,n\}^2 $ uniformly at random. Let $\omega = (G_\code e_{i_X}, G_\code e_{i_Z})$ and $\gamma =  (G_\code e_{i_X}) \cdot(G_\code e_{i_Z}) \in \field$.
		\begin{enumerate}
		\item If $\gamma=0$ then select a pair of questions $(x_c,y_c)$ as in the commutation game. Send $(x_c,\omega)$ to $\alice$ and $(y_c,\omega)$ to Bob. Accept if and only if their answers are accepted in the commutation game. 
		\item If $\gamma\neq 0$ then do the same but for the anti-commutation game. 
		\end{enumerate} 
		 \item (\textbf{Consistency test}) Select $(i_X,i_Z)\in \{1,\ldots,n\}^2 $ and $W\in \{X,Z\}$ uniformly at random. Let $\omega=(G_\code e_{i_X}, G_\code e_{i_Z})$ and $\gamma = (G_\code e_{i_X}) \cdot(G_\code e_{i_Z}) \in \field$. Send $(W,i_W)$ to $\alice$ and $(x_{W,\gamma},\omega)$ to $\bob$. Receive $a\in \field$ and $b\in \field$ respectively. Accept if and only if $a=b$. 
    \end{enumerate}
  \end{gamespec}
  \caption{The braiding test over $\code$ verifies that the players respond consistently with a uniformly random codeword from $\code$, obtained by measuring $k$ shared EPR pairs in the standard or Hadamard basis and encoding the resulting $k$-bit string.}
  \label{fig:braiding-test}
\end{figure}

@@

\begin{theorem}
Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$ that is $\delta(\eps)$-quantum sound. Then the braiding test over $\code$ is a $(k,\delta')$-qubit test, where $S_X=S_Z=\{G_\code e_i:\,i\in\{1,\ldots,n\}\}\subseteq \field^k$, $\phi(W,G_\code e_i)=(W,i)$ and $\delta' = O(\sqrt{r}\delta^{1/4}(12\eps))$.\footnote{Assume $G_\code$ has no repeated columns.} 
\end{theorem}

\begin{proof}
\underline{Completeness:} We first verify completeness. For $W\in\{X,Z\}$ and $i\in\{1,\ldots,n\}$ let $P^{(W,i)}_a = (\tau^W(G_\code e_i))_a$ and $P^{(W,S)}_a = \prod_{i\in S} P^{(W,i)}_{a_i}$. For $(i_X,i_Z)\in \{1,\ldots,n\}^2 $ let $\omega=(G_\code e_{i_X}, G_\code e_{i_Z})$ and $\gamma =(G_\code i_X) \cdot(G_\code {i_Z}) $ we let $P^{x_{W,\gamma},\omega} = P^{(W,i_W)}$.

@@

\underline{Soundness:} Next we show soundness. Let $\strategy$ be a synchronous strategy for $G$  in  $(\mM,\tau)$ that succeeds with probability at least $1-\eps$. For $W\in\{X,Z\}$ let $\strategy^W$ be the strategy in $G_{\code,M}$ that is obtained by restricting $\strategy$ to the relevant measurements, i.e.\ the $P^{W,S}$ and $P^{W,i}$.  Then $\strategy^W$ succeeds with probability at least $1-6\eps$ in $G_{\code,M}$. Using the assumption that $M$ is $\delta(\cdot)$-quantum sound and the first item from Proposition~\ref{prop:sound-game} it follows that there is a $\delta_1 = O(r\sqrt{\delta(12\eps)})$ such that for each $W\in\{X,Z\}$, $\strategy^W$ is $(\delta_1,\mu)$ close to a perfect strategy $\tilde{\strategy}^W$ on $(\mN^W,\tau^W)$. This strategy in particular has measurement operators $\{ \tilde{P}^{W,S}_a\}$ and $\{\tilde{P}^{W,i}_b\}$ associated with questions of the form $S$ and $i$ in $G_{\code,M}$. Since $(\code,M)$ is Abelian, there is a  POVM $\{\tilde{P}^W_u\}_{u\in \field^n}$ such that $\sum_{u\in \code}\tilde{P}^W_u = \Id$ and for each $i\in \{1,\ldots,n\}$, $\tilde{P}^{W,i}_b = \sum_{a:a\cdot u_i=b} \tilde{P}^W_a$ where  $u_i = G_\code e_i$.

Applying Lemma~\ref{lem:pull-back}, we obtain projective measurements $\{Q^W_u\}$ on $\mM$ such that 
\begin{equation*}
\sum_u \big\|Q^W_u - (w^W)^* \tilde{P}_u^W w^W \big\|^2_2 \,=\, O(\delta_1)\;.
\end{equation*}
For any $i\in\{1,\ldots,n\}$ let $Q^{W,i}_b = \sum_{a:\,a\cdot u_i=b}  Q^W_a$. Then by Lemma~\ref{lem:dp},
\begin{align*}
\Es{i}\sum_b \tau\big( Q^{W,i}_b (w^W)^*\tilde{P}^{W,i}_b(w^W) \big)
&\geq \Es{i}\sum_a \tau\big( Q^{W}_a (w^W)^*\tilde{P}^{W}_a(w^W) \big)\\
&\geq 1-O(\delta_1)\;.
\end{align*}
Applying Lemma~\ref{lem:close-value} we deduce that the strategy that consists of $Q^X$, $Q^Z$, $P^{x_c,\omega}$ for $(x_c,\omega) \in \mX_{com}\times \Omega_+$ and $P^{x_{ac},\omega}$ for $(x_{ac},\omega)\in \mX_{anticom} \times \Omega_-$ succeeds in the game $G_{\dlS}$ with probability $1-O(\sqrt{\delta_1})$. Applying~\cite[Corollary 3.9]{de2022spectral}, the conclusion follows. 
\end{proof}
